Inferring the gravitational potential of the Milky Way with a few precisely measured stars

### 2014-02-12 text/paper2/ms.tex
filling in comparison

@@

The difficulty and computational costs associated with proper N-body modeling has motivated numerous efforts for developing approximate methods for constraining properties of the Galactic potential with cold debris structures. The simplest approximation is to fit a single orbit to observed debris \citep[e.g.,][]{koposov10, deg13}. This has the advantage of naturally incorporating observational errors, but is known to be invalid as debris does not exactly follow an orbit \citep[e.g.,][]{binney08, eyre11, sanders13a}. To account for this, methods have been proposed that model the debris as an orbit plus some dispersion or offset in phase space \citep[e.g.,][]{eyre09a, varghese11, kuepper12} and action-angle coordinates \citep{eyre11, sanders13b, bovy14}. Other statistical methods have been proposed \citep[][]{penarrubia12, sanderson14} that may prove powerful when applied to, e.g., data from the \gaia mission, where full 6D coordinates will be known for large samples of stars in the halo --- and therefore many debris structures --- but membership is not necessarily known. However, these methods do not account for observational errors.

In methods that rely on action-angle coordinates, [...].

@@

\section{...}

>>>>

\newcommand{\paperone}{Paper 1}

@@

The difficulty and computational costs associated with proper N-body modeling has motivated numerous efforts for developing approximate methods for constraining properties of the Galactic potential with cold debris structures. The simplest approximation is to fit a single orbit to observed debris \citep[e.g.,][]{koposov10, deg13}. This has the advantage of naturally incorporating observational errors, but is known to be invalid as debris does not exactly follow an orbit \citep[e.g.,][]{binney08, eyre11, sanders13a}. To account for this, methods have been proposed that model the debris as an orbit plus some dispersion or offset in phase space \citep[e.g.,][]{eyre09a, varghese11, kuepper12} or action-angle coordinates \citep{eyre11, sanders13b, bovy14}. Other statistical methods have been proposed \citep[][]{penarrubia12, sanderson14} that may prove powerful when applied to, e.g., data from the \gaia mission, where full 6D coordinates will be known for large samples of stars in the halo --- and therefore many debris structures --- but membership is not necessarily known. However, these methods do not account for observational errors.

Methods that rely on action-angle coordinates, [...]. Any generative model that relies on matching densities --- whether in phase-space, action-space, or observed coordinates --- must also include details about the progenitor and a model for the background of stars. [...] In \citet[][hereafter \paperone]{apw13}, we introduced a simple method for using individual stars combined with knowledge about the mass and orbit of the progenitor to constrain properties of the host galaxy potential (\emph{Rewinder}). [...]

@@

\section{Method}
